% Footnotes used inline in the text.
\newcommand{\manualhandlingfootnote}{\footnote{\url{http://www.hse.gov.uk/pubns/indg143.pdf}}}
\newcommand{\chargingfootnote}{\footnote{\url{http://docs.sourcebots.co.uk/kit/batteries/charging/}}}
\newcommand{\estatesfacilitiesfootnote}{\footnote{Estates and Facilities: \url{http://www.southampton.ac.uk/estates/}}}


\newcommand{\groupname}{Student Robotics (Southampton)}
\newcommand{\assessorname}{Kier Davis}
\newcommand{\assessoremail}{me@kierdavis.com}
\newcommand{\assessmentdate}{April 12, 2018}


\newcommand{\activityname}{SourceBots - Competition}
\newcommand{\activitydate}{April 20 to April 22, 2018}
\newcommand{\activitytime}{All day}
\newcommand{\activitylocation}{The Cube, Bar Two, Bar Three}
\newcommand{\activitysummary}{
    This event is part of a four-month outreach programme based at the
    university in which teams of students from local schools compete to design,
    build and test autonomous robots. The robots must perform the simple task of
    locating and moving marked boxes around an arena.

    The programme is run by the informal volunteer organisation SourceBots, who
    will be considered event staff.

    Competitors are aged 16--18 and will be supervised at all times by at least
    one responsible adult (typically a teacher from the school) per team. We
    expect 9 teams and 10--20 SourceBots volunteers to attend the event.

    First-aiders are present among staff and will be identified to other
    attendees of the event.
}


\newcommand{\references}{
    \reference{Guidance from the Health and Safety Executive, including manual
    handling procedures. \\
    \url{http://www.hse.gov.uk/risk/index.htm}}

    \reference{H\&S guidance from the Union Southampton website. \\
    \url{https://www.unionsouthampton.org/groups/admin/howto/protection}}

    \reference{Lithium polymer battery charging procedure, available on the
    SourceBots website. \\
    \url{http://docs.sourcebots.co.uk/kit/batteries/charging/}}
}


\newcommand{\risks}{
    \risk
        {Manual handling of heavy objects}
        {Competitors or staff could experience minor injury or back pains
         resulting from improper lifting methods.}
        {\item The HSE manual handling guidelines\manualhandlingfootnote are to
         be followed for all tasks involving heavy lifting.
         \item Of particular note is that due to space arrangements some teams
         will be required to frequently transport unwieldy items (their robots)
         between floors of the building. Elevators should be used for this when
         possible; in the event of elevator failure, extra caution must be taken
         when using the stairs.}
        {\item All attendees to be made aware of the locations of the building's
         elevators.}
        {1} % Likelihood (/3)
        {2} % Impact (/3)

    \risk
        {Obstacles on the floor, such as bags, boxes or trailing cables}
        {Competitors, supervisors or staff may suffer injury as a result of
         tripping.}
        {\item Cables (such as laptop power supplies) will be routed underneath
         desks wherever possible.
         \item Cables that cannot be routed under desks will be clearly marked
         to increase their visibility.
         \item Bags, boxes and other items that are potential trip hazards will
         be stacked neatly by the walls whenever possible.}
        {\item No further action required.}
        {2} % Likelihood (/3)
        {1} % Impact (/3)

    \risk
        {Lithium polymer batteries}
        {LiPo batteries can ignite if damaged or misused, resulting in
         smoke/fire.}
        {\item Boxes containing batteries are clearly labelled as such and will
         be handled with care at all times.
         \item Batteries will be routinely inspected by staff for signs of
         damage or swelling, and set aside for safe disposal if necessary.
         \item Batteries are only to be charged by trained staff. The battery
         charging procedure\chargingfootnote is to be followed at all times.
         \item Batteries are only to be given to teams once their robot has
         passed a safety inspection by a member of staff. This inspection must
         check, among other things, that the robot's battery compartment is
         rigid enough to resist damage to the battery.}
        {\item No further action required.}
        {1} % Likelihood (/3)
        {2} % Impact (/3)

    \risk
        {Interaction with autonomous robots/robotics equipment}
        {Competitors, supervisors or staff could encounter minor injuries if the
         robots' actuators move unexpectedly.}
        {\item Robots are only to be tested under supervision.
         \item When robotics equipment is switched on, it will be treated as
         though its actuators could become active at any moment.
         \item The arena is to be supervised by a member of staff at all times.
         Robots must pass a safety inspection before being allowed into the
         arena.}
        {\item Staff will verify that the robotics equipment does not present
         any sharp edges. If any are found, they will be removed, covered, or
         otherwise modified to reduce the chance and severity of injury they
         could cause.}
        {1} % Likelihood (/3)
        {1} % Impact (/3)

    \risk
        {Electrical equipment (robots, computers, battery chargers, stage
         lighting/sound equipment)}
        {Competitors, supervisors or staff could get electrical shocks or burns
         from faulty equipment.}
        {\item Computing equipment, battery chargers and other mains-powered
         equipment has been PAT tested.
         \item Opened food and drink is prohibited in the vicinity of computers
         and robotics equipment.}
        {\item Staff will verify that all wiring done by teams or already
         preexisting in the robotics kit is sufficiently insulated and robust
         before the robotics kit is allowed to be switched on.}
        {1} % Likelihood (/3)
        {2} % Impact (/3)

    \risk
        {Use of manual and/or power tools}
        {Competitors or staff could experience minor injury as a result of an
         accident or through improper use of tools.}
        {\item Care will be taken with tools to ensure that minimal injury
         results in the event of an accident.
         \item Power tools are only to be used by competitors while under
         supervision by a responsible adult.}
        {\item No further action required.}
        {2} % Likelihood (/3)
        {1} % Impact (/3)

    \risk
        {Soldering}
        {Competitors may suffer burns through inappropriate use of soldering
         irons. Soldering may produce fumes which can lead to asthma.}
        {\item All soldering irons are to be treated as if they are hot even if
         they are unplugged (since they may still be cooling down).
         \item Soldering will only be permitted in rooms with appropriate
         ventilation.
         \item Safety glasses are to be worn when soldering.}
        {\item No further action required.}
        {1} % Likelihood (/3)
        {2} % Impact (/3)
}


\newcommand{\postrisks}{
    \subsection*{Risk of fire}

    To minimise the risk of fire resulting from this activity, food and drink
    will not be allowed near electrical equipment, and naked flames will be
    prohibited. The risk of fire occurring elsewhere in the building(s) is
    controlled primarily by the building operator\estatesfacilitiesfootnote.
    Staff will ensure that all people present are informed of the locations of
    the exits and whether any fire drills are expected to take place. Should a
    fire break out (or any other event requiring evacuation), all people are to
    evacuate through the nearest accessible exit.
}


\input{../../template.tex}
