% Footnotes used inline in the text.
\newcommand{\manualhandlingfootnote}{\footnote{\url{http://www.hse.gov.uk/pubns/indg143.pdf}}}
\newcommand{\chargingfootnote}{\footnote{\url{https://www.studentrobotics.org/docs/kit/batteries/imax_b6_charger\#ChargingChecklist}}}
\newcommand{\estatesfacilitiesfootnote}{\footnote{Estates and Facilities: \url{http://www.southampton.ac.uk/estates/}}}
\newcommand{\esofootnote}{\footnote{Equipment and Safety Officer; for the duration of this event, this role will be filled by Kier Davis (\email{me@kierdavis.com}).}}


\newcommand{\groupname}{Student Robotics (Southampton)}
\newcommand{\assessorname}{Kier Davis}
\newcommand{\assessoremail}{me@kierdavis.com}
\newcommand{\assessmentdate}{July 6, 2016}


\newcommand{\activityname}{Summer School (general activities)}
\newcommand{\activitydate}{August 1 to August 5, 2016}
\newcommand{\activitytime}{All day}
\newcommand{\activitylocation}{Lecture Theatre 2A/2077,
                               Seminar Room 53/4025,
                               Zepler L2 Labs (Building 59),
                               Zepler L3 Labs (Building 59),
                               The Cube}
\newcommand{\activitysummary}{
    The summer school is run by the ECS department with assistance from
    Student Robotics Southampton. The participants in the summer school are
    invited to design, build and test an autonomous robot in small teams. The
    robots must perform a simple task, usually involving locating and moving
    coloured boxes, which is performed competitively against other teams'
    robots.

    In addition to this main event, there are a number of taught laboratory
    sessions. Members of Student Robotics Southampton will mentor and provide assistance to
    the participants, as well as set up the arena for the competition and lead
    the laboratory sessions.

    This risk assessment covers general practical activities performed during
    the setup and execution of the summer school. These include transporting
    equipment from storage to the various venues used for the summer school, as
    well as administrative tasks.

    Separate risk assessments are maintained for the use of electronics
    laboratories for taught laboratory sessions and robot construction, and the
    use of the Cube for the competition itself.
}


\newcommand{\references}{
    \reference{Guidance from the Health and Safety Executive, including manual
    handling procedures. \\
    \url{http://www.hse.gov.uk/risk/index.htm}}

    \reference{H\&S guidance from the Union Southampton website. \\
    \url{https://www.unionsouthampton.org/groups/admin/howto/protection}}

    \reference{Risk assessments prepared for events run by Student Robotics in 2015. \\
    \url{https://github.com/srobo-southampton/risk-assessments/tree/master/old}}

    \reference{Lithium polymer battery charging procedure, available on the
    Student Robotics website. \\
    \url{https://www.studentrobotics.org/docs/kit/batteries/imax_b6_charger\#ChargingChecklist}}
}


\newcommand{\risks}{
    \risk
        {Manual handling of heavy objects}
        {Competitors or mentors could experience minor injury or back pains
         resulting from improper lifting methods.}
        {\item The HSE manual handling guidelines\manualhandlingfootnote are to
         be followed for all tasks involving heavy lifting.}
        {\item No further action required.}
        {1} % Likelihood (/3)
        {2} % Impact (/3)

    \risk
        {Obstacles on the floor, such as bags, boxes or trailing cables}
        {Competitors or mentors may suffer injury as a result of tripping.}
        {\item Cables (such as laptop power supplies) will be routed underneath
         desks wherever possible.
         \item Cables that cannot be routed under desks will be clearly marked
         to increase their visibility.
         \item Bags, boxes and other items that are potential trip hazards will
         be stacked neatly by the walls whenever possible.}
        {\item No further action required.}
        {2} % Likelihood (/3)
        {1} % Impact (/3)

    \risk
        {Lithium polymer batteries}
        {LiPo batteries can ignite if damaged or misused, resulting in
         smoke/fire.}
        {\item Boxes containing batteries are clearly labelled as such and will
         be handled with care at all times.
         \item Batteries will be routinely inspected by mentors for signs of
         damage or swelling, and set aside for safe disposal if necessary.
         \item Batteries are only to be charged by trained mentors. The battery
         charging procedure\chargingfootnote is to be followed at all times.}
        {\item No further action required.}
        {1} % Likelihood (/3)
        {2} % Impact (/3)
}


\newcommand{\postrisks}{
    \subsection*{Risk of fire}

    To minimise the risk of fire resulting from this activity, food and drink
    will not be allowed near electrical equipment, and naked flames will be
    prohibited. The risk of fire occurring elsewhere in the building(s) is
    controlled primarily by the building operator\estatesfacilitiesfootnote.
    The ESO\esofootnote will ensure that all people present are informed of the
    locations of the exits and whether any fire drills are expected to take place.
    Should a fire break out (or any other event requiring evacuation), all
    people are to evacuate through the nearest accessible exit.
}


\input{../../template.tex}
