% Footnotes used inline in the text.
\newcommand{\manualhandlingfootnote}{\footnote{\url{http://www.hse.gov.uk/pubns/indg143.pdf}}}
\newcommand{\chargingfootnote}{\footnote{\url{https://www.studentrobotics.org/docs/kit/batteries/imax_b6_charger\#ChargingChecklist}}}
\newcommand{\estatesfacilitiesfootnote}{\footnote{Estates and Facilities: \url{http://www.southampton.ac.uk/estates/}}}
\newcommand{\esofootnote}{\footnote{Equipment and Safety Officer; for the duration of this event, this role will be filled by Kier Davis (\email{me@kierdavis.com}).}}


\newcommand{\groupname}{Student Robotics (Southampton)}
\newcommand{\assessorname}{Kier Davis}
\newcommand{\assessoremail}{me@kierdavis.com}
\newcommand{\assessmentdate}{July 6, 2016}


\newcommand{\activityname}{Summer School (laboratories)}
\newcommand{\activitydate}{August 1 to August 5, 2016}
\newcommand{\activitytime}{All day}
\newcommand{\activitylocation}{Zepler L2 Labs (Building 59),
                               Zepler L3 Labs (Building 59)}
\newcommand{\activitysummary}{
    The summer school is run by the ECS department with assistance from
    Student Robotics Southampton and funded by the Smallpeice Trust.
    The participants in the summer school are
    teenagers in Year 12 (age 16--17), and are
    invited to design, build and test an autonomous robot in small teams. The
    robots must perform a simple task, usually involving locating and moving
    coloured boxes, which is performed competitively against other teams'
    robots.

    In addition to this main event, there are a number of taught laboratory
    sessions. Members of Student Robotics Southampton will mentor and provide assistance to
    the participants, as well as set up the arena for the competition and lead
    the laboratory sessions.

    The summer school participants are to be supervised by DBS-checked staff
    from the Smallpeice Trust at all times. As a result it is not a requirement
    for ECS and Student Robotics Southampton staff to have DBS certificates;
    however it is still advantageous to have one. The supervision staff include
    trained first-aiders.

    This risk assessment specifically covers the use of the electronics and
    computing laboratories for taught lab sessions and robot
    building sessions. Manual and/or power tools will be used to assemble the
    robot chassis, and lithium polymer batteries may be used inside the robots.
    The Level 3 labs are only used for the taught programming laboratory (which
    only involves using the workstations there). All other activities (those
    involving robots, electronics, etc.) take place in the Level 2 electronics
    labs.

    This document should be considered an extension of the general risk
    assessment for the summer school\footnote{Available at
    \url{http://dl.kierdavis.com/srobo-soton-risk-assessments/latest/20160801-summer-school.pdf}}.
}


\newcommand{\references}{
    \reference{Guidance from the Health and Safety Executive, including manual
    handling procedures. \\
    \url{http://www.hse.gov.uk/risk/index.htm}}

    \reference{H\&S guidance from the Union Southampton website. \\
    \url{https://www.unionsouthampton.org/groups/admin/howto/protection}}

    \reference{Risk assessments prepared for events run by Student Robotics in 2015. \\
    \url{https://github.com/srobo-southampton/risk-assessments/tree/master/old}}

    \reference{Lithium polymer battery charging procedure, available on the
    Student Robotics website. \\
    \url{https://www.studentrobotics.org/docs/kit/batteries/imax_b6_charger\#ChargingChecklist}}

    \reference{General ECS Teaching Lab Risk Assessment (attached)}
}


\newcommand{\risks}{
    \risk
        {Manual handling of heavy objects}
        {Competitors, mentors or staff could experience minor injury or back pains
         resulting from improper lifting methods.}
        {\item The HSE manual handling guidelines\manualhandlingfootnote are to
         be followed for all tasks involving heavy lifting.}
        {\item No further action required.}
        {1} % Likelihood (/3)
        {2} % Impact (/3)

    \risk
        {Interaction with autonomous robots}
        {Competitors, mentors or staff could encounter minor injuries if the robots
         move unexpectedly.}
        {\item Robots are only to be tested under supervision.
         \item When robots are switched on, they will be treated as though they
         could become active at any moment.}
        {\item The ESO\esofootnote will verify that the robots do not present
         any sharp edges. If any are found, they will be remove, covered, or
         otherwise modified to reduce the chance and severity of injury they
         could cause.}
        {1} % Likelihood (/3)
        {1} % Impact (/3)

    \risk
        {Use of manual and/or power tools}
        {Competitors or mentors could experience minor injury as a result of an
         accident or through improper use of tools.}
        {\item Care will be taken with tools to ensure that minimal injury
         results in the event of an accident.
         \item Power tools are only to be used by competitors while under
         supervision by a responsible adult.}
        {\item No further action required.}
        {2} % Likelihood (/3)
        {1} % Impact (/3)

    \risk
        {Soldering}
        {Competitors may suffer burns through inappropriate use of soldering
         irons. Soldering may produce fumes which can lead to asthma.}
        {\item If soldering irons are to be used during the taught laboratories,
         a demonstration of correct technique will be performed beforehand by an
         experienced mentor.
         \item All soldering irons are to be treated as if they are hot even if
         they are unplugged (since they may still be cooling down).
         \item Soldering will only be permitted in rooms with appropriate
         ventilation.
         \item Safety glasses are to be worn when soldering.}
        {\item No further action required.}
        {1} % Likelihood (/3)
        {2} % Impact (/3)

    \risk
        {Electrical equipment (robots, computers, battery chargers)}
        {Competitors, mentors or staff could get electrical shocks or burns from faulty
         equipment.}
        {\item Computing equipment, battery chargers and other mains-powered
         equipment have been PAT tested.
         \item Opened food and drink are prohibited inside the laboratory.}
        {\item The ESO will verify that all wiring in the robots is sufficiently
         insulated before they are allowed to be tested.}
        {1} % Likelihood (/3)
        {2} % Impact (/3)

    \risk
        {Obstacles on the floor, such as bags, boxes or trailing cables}
        {Competitors, mentors or staff may suffer injury as a result of tripping.}
        {\item Cables (such as laptop power supplies) will be routed underneath
         desks wherever possible.
         \item Cables that cannot be routed under desks will be clearly marked
         to increase their visibility.
         \item Bags, boxes and other items that are potential trip hazards will
         be stacked neatly by the walls or underneath desks whenever possible.}
        {\item No further action required.}
        {2} % Likelihood (/3)
        {1} % Impact (/3)

    \risk
        {Lithium polymer batteries}
        {LiPo batteries can ignite if damaged or misused, resulting in
         smoke/fire.}
        {\item Boxes containing batteries are clearly labelled as such and will
         be handled with care at all times.
         \item Batteries will be routinely inspected by mentors for signs of
         damage or swelling, and set aside for safe disposal if necessary.
         \item Batteries are only to be charged by trained mentors. The battery
         charging procedure\chargingfootnote is to be followed at all times.
         \item Batteries are only to be given to teams once their robot has
         passed a safety inspection by a mentor. This inspection must check,
         among other things, that the robot's battery compartment is rigid
         enough to resist damage to the battery.}
        {\item No further action required.}
        {1} % Likelihood (/3)
        {2} % Impact (/3)
}


\newcommand{\postrisks}{
    \subsection*{Other potential hazards in the laboratory}

    Users of the laboratory should be aware of all hazards in the laboratory,
    even if they are not expected to be directly related to the activity. These
    include potential exposure to chemicals, high voltages/currents, high
    temperatures and sharps. The general ECS Teaching Lab risk assessment
    (attached) should be referred to for specific details of these hazards and
    the control measures in place.

    \subsection*{Risk of fire}

    To minimise the risk of fire resulting from this activity, opened food and
    drink will not be allowed inside the laboratory, and naked flames will be
    prohibited. The risk of fire occurring elsewhere in the building(s) is
    controlled primarily by the building operator\estatesfacilitiesfootnote.
    The ESO will ensure that all people present are informed of the locations of
    the exits and whether any fire drills are expected to take place.
    Should a fire break out (or any other event requiring evacuation), all
    people are to evacuate through the nearest accessible exit.
}


\input{../../template.tex}
