% Footnotes used inline in the text.
\newcommand{\manualhandlingfootnote}{\footnote{\url{http://www.hse.gov.uk/pubns/indg143.pdf}}}
\newcommand{\chargingfootnote}{\footnote{\url{https://www.studentrobotics.org/docs/kit/batteries/imax_b6_charger\#ChargingChecklist}}}
\newcommand{\estatesfacilitiesfootnote}{\footnote{Estates and Facilities: \url{http://www.southampton.ac.uk/estates/}}}
\newcommand{\esofootnote}{\footnote{Equipment and Safety Officer; for the duration of this event, this role will be filled by Kier Davis (\email{me@kierdavis.com}).}}


\newcommand{\groupname}{Student Robotics (Southampton)}
\newcommand{\assessorname}{Kier Davis}
\newcommand{\assessoremail}{me@kierdavis.com}
\newcommand{\assessmentdate}{June 21, 2016}


\newcommand{\activityname}{Summer School (use of Mountbatten building)}
\newcommand{\activitydate}{August 1 to August 5, 2016}
\newcommand{\activitytime}{All day}
\newcommand{\activitylocation}{Room 53/4025 (Mountbatten building)}
\newcommand{\activitysummary}{
    The summer school is run by the ECS department with assistance from the
    Student Robotics organisation. The participants are invited to design,
    build and test an autonomous robot to perform a complex task. In addition to
    this main event, there are a number of taught laboratory sessions. Members
    of Student Robotics will mentor and provide assistance to the participants,
    as well as set up the arena for the competition and lead the laboratory
    sessions.

    This risk assessment only covers the use of the room 53/4025, which is used
    for access to the storage cupboard.
}


\newcommand{\references}{
    \reference{Guidance from the Health and Safety Executive, including manual
    handling procedures. \\
    \url{http://www.hse.gov.uk/risk/index.htm}}

    \reference{H\&S guidance from the Union Southampton website. \\
    \url{https://www.unionsouthampton.org/groups/admin/howto/protection}}

    \reference{Risk assessments prepared for events run by Student Robotics in 2015. \\
    \url{https://github.com/srobo-southampton/risk-assessments/tree/master/old}}

    \reference{Lithium polymer battery charging procedure, available on the
    Student Robotics website. \\
    \url{https://www.studentrobotics.org/docs/kit/batteries/imax_b6_charger\#ChargingChecklist}}
}


\newcommand{\risks}{
    \risk
        {Manual handling of heavy objects}
        {Mentors could experience minor injury or back pains resulting from
         improper lifting methods.}
        {\item The HSE manual handling guidelines\manualhandlingfootnote are to
         be followed for all tasks involving heavy lifting.}
        {\item No further action required.}
        {1} % Likelihood (/3)
        {2} % Impact (/3)

    \risk
        {Obstacles on the floor, such as bags, boxes or trailing cables}
        {Mentors may suffer injury as a result of tripping.}
        {\item Cables (such as laptop power supplies) will be routed underneath
         desks wherever possible.
         \item Cables that cannot be routed under desks will be clearly marked
         to increase their visibility.
         \item Bags, boxes and other items that are potential trip hazards will
         be stacked neatly by the walls whenever possible.}
        {\item No further action required.}
        {2} % Likelihood (/3)
        {1} % Impact (/3)

    \risk
        {Lithium polymer batteries}
        {LiPo batteries can ignite if damaged or misused, resulting in
         smoke/fire.}
        {\item Batteries will be routinely inspected for signs of damage or
         swelling, and set aside for safe disposal if necessary.
         \item Batteries are only to be charged by trained mentors. The battery
         charging procedure\chargingfootnote is to be followed at all times.}
        {\item No further action required.}
        {1} % Likelihood (/3)
        {2} % Impact (/3)
}


\newcommand{\postrisks}{
    % \newpage

    \subsection*{Risk of fire}

    To minimise the risk of fire resulting from this activity, food and drink
    will not be allowed near electrical equipment, and naked flames will be
    prohibited. The risk of fire occurring elsewhere in the building is
    controlled primarily by the building operator\estatesfacilitiesfootnote.
    The ESO\esofootnote will ensure that all people present are informed of the
    locations of the exits and that no fire drills are expected to take place.
}


\input{../../template.tex}
